The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-29 paper/ms.tex
moved dust extinction subsection into obs part

All magnitudes are in AB system.
\section{Observational Datasets}
\label{sec:theo}

@@

The starting point for this medho is a population of dark matter halos.
To each halo we assign a UV luminosity according to the following
parameterization.
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1},
  \end{equation}
where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are two slopes corresponding to the faint and
bright end, respectively. 
This equation has the same functional dependence as stellar to dark
mass ratio used by \citet{Moster10}.

The relation between UV luminosity and Star Formation Rate
\citep{Madau98,Kennicutt98} 
is given by:
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right)
\end{equation}

  With Initial Mass Function (IMF) between $0.1 M_\odot$ 
 and $100 M_\odot$, in the range of $1250-2500 \mathring{\textrm{A}} $

The star forming rate will be:
  \begin{equation}
  SFR = k \times L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1}
  \end{equation}

We use the dark matter halo catalog from the Big MultiDark Plank 1 (MDPL) 
Simulation \citep{Klypin14} with 2013 Planck cosmology \citep{Planck1}. MDPL is 
quite similar to the Big Bolshoi ($1 \textrm{Gpc h}^{-1}$) \citep{Prada12} and 
its predecesor Bolshoi \citep{Klypin11} ($250 \textrm{Mpc h}^{-1}$), booth of 
them with WMAP5 cosmology, but MDPL has bigger mass resolution.  Those halo 
catalogs are available at the MultiDark 
Database\footnote{\url{http://www.multidark.org}} \citep{Riebe13}.

The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
code. The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ side 
length. It has $3840^3$ dark matter particles of  $1.51\times 9
\textrm{M}_{\odot} \textrm{h}^{-1}$ mass each one. The 2013 Planck
cosmology is defined by the following parameters: $\Omega_M = 0.307$,
$\Omega_B = 0.048$, $\Omega_\Lambda = 0.730$, $\sigma_8 = 0.829$, $n_s
= 0.96$ and  $H_0 = 67.8$. The DMH Catalog at $z=6$ contains $\sim
10.9 \times 10^7$   halos, to avoid incompleteness in the low mass
end, halos with mass below   $10^{10.3} \textrm{M}_{\odot}
\textrm{h}^{-1}$ are rejected. In order to study how  
cosmic variance can affect measurements, the original catalog is
divided into 64 small   cubic boxes, with a similar volume to the
observations.

The following treatment is applied to every one small box.

The halo abundance matching technique has been widely used \citep{Colin99, 
Kravtsov04} resulting in good reproduction of the observed galaxy clustering. 
\citep{Conroy06, Lee09}. Here we use the simplest case with few premises: 
\begin{enumerate}
 \item Each halo in the catalog hosts one galaxy. There are not empty
halos, also none of halos has two or more galaxies.
 \item The UV luminosity of each galaxy is function of one variable; the mass of
the DMH in which is located. This function must be monotone, this guarantees that most 
massive halos will host the most luminous galaxies in the same volume.
\end{enumerate}

@@

Dust in star forming galaxies absorbs part of the UV radiation and reemits on IR. The more 
massive is the galaxy then more dust contains and dust attenuation will be greater. The 
relation between dust attenuation and magnitude have been already studied, with this relation 
we can infer the dust-free UV luminosity of a galaxy from observations, resulting in  a more 
accurate inferred SFR.

@@

>>>>

All magnitudes are in AB system.
\section{Observational Constraints}
\label{sec:theo}

@@

@@

Dust present in these high redshift star forming galaxies can
attenuate the UV intrinsic luminosity.
Although relatively uncertain compared to studies in the local
universe, there are constraints on the extinction level in LBGs at
$z=6$.

@@

The starting point for this method is a population of dark matter halos.
To each halo we assign a UV luminosity according to the following
parameterization.
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1},
  \end{equation}
where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are two slopes corresponding to the faint and
bright end, respectively. 
We now that this equation has the same functional dependence suggested
 by \citet{Moster10} to link stellar and dark matter masses.

Once each halo has a UV luminosity we also have the option to include
an extinction correction in order to modify this intrinsic luminosity
vale. 
From these UV values we build the LF.
The free parameters in Eq. (\ref{eqn:luminosity}) are determined by
requiring that the abudance matching LF follows the observational
constraints. 
Then we use the following relationship between UV luminosity and Star Formation Rate
\citep{Madau98,Kennicutt98} 
\begin{equation}
 \textrm{SFR}\left(M_\odot \textrm{yr}^{-1}\right) 
      = 1.4 \times 10^{-28} L_{\nu} \left( \textrm{erg s}^{-1}\textrm{Hz}^{-1} 
	\right), 
\end{equation}
to finally link SFR with DM halo mass.

\subsection{N-body Simulations and Halo Catalogs}

Cosmological N-body simulations are the source of the dark matter halo
populations.
We use two different simulations to cover the wide dynamical range
explored by the observations: Big MultiDark Planck (MDPL) and Planck
Bolshoi (P-Bolshoi). 
Both simulations use 2013 Planck cosmology  defined by the following
parameters: $\Omega_M = 0.307$, $\Omega_B = 0.048$, $\Omega_\Lambda =
0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and  $H_0 = 67.8$.

The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
code. 
The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ on a side.
It has $3840^3$ dark matter particles mass of $1.51\times 9
\textrm{M}_{\odot} \textrm{h}^{-1}$.
The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$   halos, to
avoid incompleteness in the low mass end, halos with mass below
$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. 
We split this large volume into 64 smaller cubic boxes of $250$\hMpc
on a side (similar volume to the observations by \citet{Willott13}) to
study the influence of cosmic variance.

The P-Bolshoi simulation...

We obtained the data from the public
database\footnote{\url{http://www.multidark.org}} \citep{Riebe13}.
